CMC Validation

### 2020-02-11 code/CMC_Validation.Rmd
CMC Validation

setEPS()
postscript("DLFPFC_Cor_gt5Perc.eps", onefile = TRUE)
  hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
dev.off()
hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
################################################################################
#CMC ACC DATA
library(stringr)

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21478397';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
thisFileName <- 'CMC_DataProcessing.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

>>>>

setEPS()
postscript("DLPFC_Cor_gt5Perc.eps", onefile = TRUE)
  hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
dev.off()
hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
################################################################################
#CMC ACC DATA
library(stringr)

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
thisFileName <- 'CMC_DataProcessing.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```
